\myTitle

### 2023-10-21 body-text-of-paper.tex
Add the Introductory motivating example

Can we say something about Anthony Almudevar's visionary method for GSI power assessment \citep{almudevar2000exact}

@@

Something here.

@@

>>>>

@@

\subsection*{An introductory motivating example}

Before we proceed to a description of the methodology used by gscramble,
we demonstrate a case in which using a standard sampling-with-replacement
approach to simulate genotypes leads to the incorrect conclusion that a set of genetic
markers is sufficient to accurately estimate admixture fractions between two populations.
To construct this simple example, we used the R programming language (CITE) to
simulate allele frequencies for $L$ biallelic
loci in a single population from a $\mathrm{Beta}(1, 8)$ distribution and then simulated
two samples, $A$ and $B$ of size $N$ diploid genotypes from this population by drawing each of the three
possible genotypes at each locus from their
expected genotype frequencies under Hardy-Weinberg equilibrium.  In this case,
each set of $N$ individuals is a sample from exactly the same population, so
there would be no basis for performing population assignment between $A$ and $B$.

However, we treated samples $A$ and $B$ as if they were sampled from two potentially different
populations, and simulated $9n$ new individuals: $n$ new individuals at each of the 9 values of
$q_A$, the admixture fraction for population $A$, in  $\{0, 0.125, 0.25, 0.375, 0.5, 0.625, 0.75, 0.875, 1.0\}$.
We then added these $9n$ to the original $2N$ individuals ($N$ from sample $A$ and $N$ from $B$)
and analyzed the genotypes using ADMIXTURE with $K=2$, doing a completely
unsupervised analysis or doing a supervised analysis in which the original $N$ samples from each
population were provided as learning samples.

For each combination $L \in \{10^2, 10^3, 10^4, 10^5\}$, 
$N \in \{25, 50, 100, 250\}$ and $n\in\{3,12,24\}$ we conducted multiple replicates
of the entire process of
simulating samples $A$ and $B$, simulating the $9n$ additional individuals, and
then analyzing them with ADMIXTURE.  We conducted sufficient replicates so that,
for each combination of $L$, $N$, and $n$ we had simulated 480 new individuals
at each $q_A$ value; thus, $160$ replicates when $n = 3$, $40$ when $n=12$, and
$20$ when $n=24$.

We hypothesized that ADMIXTURE would return estimates of $q_A$ that were
centered around the true values, even though there is no basis for that, because
the simulations were done in a na\"{i}ve way that effectively assumes that the population
allele frequencies are identical to those observed in the samples themselves. 
We further expected that ADMIXTURE would return more accurate estimates of
$q_A$ when $N$ was smaller and the number of loci was larger.
We summarized the results by plotting boxplots of the 480
ADMIXTURE-inferred $q_A$ values, for each combination of $L$, $N$, and $n$.

@@

\section*{Results}

\subsection*{An introductory motivating example}

As expected, the perceived ability to estimate $q_A$ with ADMIXTURE was higher
for larger values of $L$ and for smaller values of $N$ (Figure~\ref{fig:bias-sims}).  
%%%
\begin{figure*}
\includegraphics[width=\textwidth]{figures/bias-sims-unsup-and-sup.pdf}
\caption{ADMIXTURE estimates of $q_A$ as described in
{\em An introductory motivating example} In these results, the ability to estimate $q_A$
is a product of a bias.
}
\label{fig:bias-sims}
\end{figure*}
%%%
It is interesting to note
that, for numbers of loci,  $L$, that are 100 (or smaller) the effect is observed only when
sample size, $N$, is as small as 25---and even then the effect is slight.  However, when the
number of markers increases to 100,000---values that are becoming commonplace with the availability of chip-
or sequencing-based approaches---it is apparent that the sampling-with-replacement approach
induces an extreme bias.  With 100,000 markers, even if sample sizes are as large as 250 individuals,
using na\"{i}ve simulations improperly indicate that admixture fractions of individuals can be
accurately estimated, even when there are no genetic differences, whatsoever between the populations that
samples $A$ and $B$ are drawn.
